Bayesian Insights into Aerial Bombing Strategies: An Ordered Logistic Regression Analysis of WWII Target Prioritization Against Germany

### 2024-04-18 paper/paper.qmd
modify vague sentences

Prospects for future research based on this dataset are immense. One could investigate whether there were unwritten standards during World War II for minimizing civilian harm, using the geographical coordinates available in the data to map bombing patterns against civilian population centers. Such analysis could offer new insights into the ethical boundaries of strategic warfare.

@@

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows a posterior prediction check, which compares the observed data (denoted by y) against the replicated data generated by the model (denoted by y_rep). The overlaid lines represent multiple posterior predictive distributions, providing a visual assessment of how well the model predictions align with the actual observed data across the range of predicted values. The close alignment between the curves indicates a good model fit, as the simulated data appears to capture the variability and central tendency of the observed data.

>>>>

Prospects for future research based on this dataset are immense. One could investigate whether there were implicit humanitarian norms upheld by nations during World War II for minimizing civilian harm, using the geographical coordinates available in the data to map bombing patterns against civilian population centers. Such analysis could offer new insights into the ethical boundaries of strategic warfare.

@@

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows a posterior prediction check, which compares the observed data *y* against the replicated data *y_rep* generated by the model. The overlaid lines represent multiple posterior predictive distributions, providing a visual assessment of how well the model predictions align with the actual observed data across the range of predicted values. The close alignment between the curves indicates a good model fit, as the simulated data appears to capture the variability and central tendency of the observed data.
